Nodal Discontinuous Galerkin Method for the Euler Equations in GR

### 2018-11-21 Documents/Euler/dgEulerGR.tex

\title{Nodal Discontinuous Galerkin Method for the Euler Equations in GR}
\author{Samuel J Dunham\altaffilmark{1}, Eirik Endeve\altaffilmark{2}, et al.}
\altaffiltext{2}{Department of Astronomy, Vanderbilt University, 6301 Stevenson Science Center, Nashville TN, 37212, USA; samuel.j.dunham@vanderbilt.edu}
\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}

>>>>

\title{Nodal Discontinuous Galerkin Method for the Euler Equations in GR}
\author{Samuel J Dunham\altaffilmark{1}, Eirik Endeve\altaffilmark{2}, et al.}
\altaffiltext{1}{Department of Astronomy, Vanderbilt University, 6301 Stevenson Science Center, Nashville TN, 37212, USA; samuel.j.dunham@vanderbilt.edu}
\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}
